Cluster Difference Imaging Photometric Survey. Vetting Report Description Document

### 2019-12-12 doc/vetting_report_documentation/doc_TeX/ms.tex
update vetting report docs for s8-s11 release

\begin{abstract}
To find planet candidates in clusters,
we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
auxiliary data.
This document describes the CDIPS planet candidate vetting reports
uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-09-18 through 2019-11-25.
\\

@@

One goal of the CDIPS project is to detect transiting planets with
known ages.  Therefore our vetting reports include information to help
assess {\it (a)} whether the transiting planet candidate is real, and
{\it (b)} whether the reported age is correct.
The code used to make these reports for the 2019-09-18 through
2019-11-25 planet candidates is available online\footnote{ 
\url{https://github.com/lgbouma/cdips/tree/a83a30}}.

Figures~\ref{fig:pg1} to~\ref{fig:pg6} summarize the document
construed for these purposes.  The planet candidate chosen for these
figures (Gaia-DR2 \texttt{5541111035713815552} = TIC
\texttt{110718787}) was chosen in part because it passed all the
tests.  It was reported\footnote{\url{https://exofop.ipac.caltech.edu/tess/view_ctoi.php}}
as a giant planet candidate in an open cluster
on Sep 9, 2019.  Higher
resolution HATSouth photometry revealed about a month afterward that
the dip signal comes from a neighboring eclipsing binary.

@@

Figure~\ref{fig:pg1}.
Periodograms from TLS and phase-dispersion minimization, calculated
with \texttt{astrobase.periodbase}, are shown in the top left and top
center
\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
The top three peaks from each method are shown in the second and third
rows; the raw light-curve is in the top-right. A small finder chart
from DSS is inset to the top left, with the 1.5-pixel radius aperture
used to extract the light-curve in orange.

@@

Figure~\ref{fig:pg2}.
Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
(\texttt{TF2}), stellar-variability detrended flux, and the background
are shown as a function of barycentric Julian date.  The overplotted
dashed vertical lines are the ephemeris of the highest-power TLS peak
from Figure~\ref{fig:pg1}.  An important visual check is whether the flux
dips are correlated with changes in the background level -- in this
case, they are not.  The standard deviation and TESS magnitude are
quoted in the upper right.  The red line in the second from the top
plot is a spline fit, which in this case an essential step for finding
the eclipse signal.

The windowed spline is an optional feature: it is only fitted and
removed if the star is found to be ``variable'' (the Lomb-Scargle peak
period is found with false alarm probability below $10^{-5}$). The
spline is a robust penalized B-spline, which is a B-spline with
knot-length automatically determined via cross-validation
\citep{eilers_flexible_1996}. The idea behind the cross-validation is
that more knots leads to smaller residuals on training data, but
larger errors when tested on the entire dataset.  We used the
\texttt{wotan} implementation, which is a wrapper to the
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
the fit residuals at each iteration
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
number of spline knots was set to 50, which for each TESS sector
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
day}$ window.

@@

Figure~\ref{fig:pg3}.
The plots show the maximally-detrended light-curve (top); the
phase-folded light-curve centered over $\pm3$ transit durations of the
primary transit (middle left); the secondary eclipse (middle right);
the odd-numbered transits (lower left); and the even-numbered transits
(lower right).  The stellar parameters ($T_{\rm eff}, R_\star,
M_\star$) are taken from TICv8 when available
\citep{stassun_TIC8_2019}.
%FIXME: if not, what happens?!?!
%Gaia-DR2 Apsis pipeline results when available
%\citep{andrae_apsis_2018}.
The first eight lines of text are parameters determined from the
best-fitting TLS model.  The one exception is the planet radius, which
uses the stellar radius as noted above.  The ``flux contamination''
(\texttt{TICCONT}) from neighboring stars is {\it never} taken into
account, because transit depth dilution does not affect image
subtraction analyses in the same manner as aperture-photometry
reductions.  The significance of the odd-to-even asymmetry is quoted,
but given the strong rotational variability in this object
(Figure~\ref{fig:pg2}), the apparent odd-even asymmetry could have
been caused by the detrending process.  To estimate the transit to
occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$, the
phase-folded light-curve is also fit by a sum of two gaussians (in
this case, the fit failed).  ``AstExc'' refers to the Gaia-DR2
astrometric excess, which can indicate hints of astrometric binarity
in the system.  ``$d_{\rm geom}$'' is the geometric distance from
\citet{bailer-jones_distances_2018}.  ``$R_\star + M_\star \rightarrow
T_{b0}$'' gives the duration of a zero-eccentricity central transit
based on the TICv8 stellar radius and mass if available. If the mass
is not available, a stellar mass is interpolated from the
\citet{pecaut_intrinsic_2013} table, under the assumption that the
star is a dwarf.
%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.

@@

Figure~\ref{fig:pg5}.
The star was considered a candidate cluster member by the source(s)
listed under ``Reference'', in this case
\citet{cantat-gaudin_gaia_2018}.  The name used in their catalog in
this case was \texttt{5599752663752776192}, a Gaia-DR2 identifier,
which can be back-referenced to find that
\citet{cantat-gaudin_gaia_2018} assigned this star a membership
probability in Haffner 13 of just 10\%.  The base catalog for the
plots is chiefly that of \citet{Kharchenko_et_al_2013}, due to its
homogeneous parameter determination procedure (particularly for age).
If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then
the remaining plots are populated.  Top-left shows the parallax, with
orange points sampled from the Gaia-DR2 posterior, black points the
other cluster members in the Kharchenko catalog, and the blue line the
claimed Kharchenko parallax for the cluster.  A number of field
contaminants in the Kharchenko catalog are visible in this case.
Top-right are the Gaia proper motions, where against black points are
cluster members from Kharchenko, and the orange is the target star.
Bottom-left is the color-magnitude diagram, and bottom-right are the
on-sky positions.  In the text, \texttt{N1sr2} is the number of
$1\sigma$ cluster members reported by \citet{Kharchenko_et_al_2013}
within the cluster angular radius; $\log t$ is the base-10 logarithm
of the age in years; \texttt{type} matches the type codes provided by
\citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the description
of the cluster from \citet{Kharchenko_et_al_2013}, if available.
Extra caution must be taken when interpreting this set of plots, since
they can only show disagreement between the observed star's properties
and those of the listed Kharchenko members (and the latter may be
biased).

@@

Figure~\ref{fig:pg6}.
This page helps diagnose which stars are producing the observed
variability.  Top-left and top-center are the mean out-of-transit
(OOT) and mean in-transit calibrated images (separate from any of our
image-subtraction analysis).  The OOT images are based on the same
number of exposures as the in-transit images and split evenly before
and after each transit
\citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
The yellow star is the target; cyan dots are the flux-weighted
centroid of the entire image for each transit event; small red crosses
are WCS-projected locations of neighbor stars.  Middle-left is the
most important sub-panel: the difference between the OOT and
in-transit mean images.  If the variability shown in background map
(units: ADU) is off-target, the transit is typically not from the
target star.  Middle-center is the same, normalized by the uncertainty
map.  Lower left and lower center show the DSS field in linear and log
scales at roughly the same pixel scale as the TESS image, with the 1,
1.5, and 2.25 pixel-radius apertures in blue, orange, and green
respectively.  The brightness of neighborhood stars is given on the
far right.  Note the slight coordinate rotation difference between DSS
and TESS images; DSS images are aligned north-up, east-left; TESS
images are oriented as closely as possible to this system without
actually performing the rotation.

\section{Neighborhood plots}

The standard vetting report's neighborhood
analysis is helpful, but insufficient for determination of
cluster membership.
A more thorough approach is to query Gaia-DR2 for
nearby stars in position, parallax, and proper motion space, and
let the data speak for itself regarding {\it (a)} the existence of
the group, and {\it (b)} the target star's membership within the group.

@@

For the 2019-09-18 through 2019-11-25 deliveries,
these plots were made with code available online\footnote{
\url{https://github.com/lgbouma/cdips_followup/tree/e4d9d}}.

\subsection{Neighborhood diagnostic}
\label{sec:nbhd}
Figure~\ref{fig:nbhd} shows the labelled quantities from
the target star, the neighborhood, and the ``cluster members'' reported by either
\citet{cantat-gaudin_gaia_2018} or \citet{Kharchenko_et_al_2013}.
The top three subplots intentionally omit the labelled
cluster members, in order to give the user their own by-eye
assessment of whether they see clusters in the neighborhood, and
whether the target star is within those clusters.

\subsection{Neighborhood diagnostic, with overplot}
\label{sec:nbdh_extra}
Figure~\ref{fig:nbhd_extra}.
Same as Figure~\ref{fig:nbhd}, but with overplotted cluster members
on the upper three subplots.

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit search summary.} See \S~\ref{sec:pg1}.
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light-curve diagnostics.} See \S~\ref{sec:pg2}.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit diagnostics.}  See \S~\ref{sec:pg3}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light-curves for increasing aperture sizes.}  See
    \S~\ref{sec:pg4}.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Cluster membership assessment diagnostics.} See
    \S~\ref{sec:pg5}.
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Imaging variability diagnostics.} See \S~\ref{sec:pg6}.
		\label{fig:pg6}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Neighborhood diagnostic.} See \S~\ref{sec:nbhd}.
		\label{fig:nbhd}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood_extra.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Neighborhood diagnostic with additional overplotted points.} See \S~\ref{sec:nbhd_extra}.
		\label{fig:nbhd_extra}
	}
\end{figure*}

>>>>

\begin{abstract}
To find planet candidates in clusters,
we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
auxiliary data.
This document describes the CDIPS planet candidate vetting reports
uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
Earlier version of this document are available at
  \url{lgbouma.com/cdips_documentation/}.
\\

@@

One goal of the CDIPS project is to detect transiting planets with
known ages.  Therefore our vetting reports include information to help
assess {\it (a)} whether the transiting planet candidate is real, and
{\it (b)} whether the reported age is correct.
The code used to make these reports is available online\footnote{
  \url{https://github.com/lgbouma/cdips/tree/57274b}}.

Figures~\ref{fig:pg1} to~\ref{fig:pg7} summarize the document
construed for these purposes.  The planet candidate chosen for these
figures (Gaia-DR2 \texttt{532542547468722176} = TIC
\texttt{401153825}) was chosen because it showcases many of the
vetting report features, while also being a likely eclipsing binary.

@@

Figure~\ref{fig:pg1}.  Periodograms from TLS and phase-dispersion
minimization, calculated with \texttt{astrobase.periodbase}, are shown
in the top left and top center
\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
The top three peaks from each method are shown in the second and third
rows; the raw light-curve is in the top-right. A finder chart
is inset to the top left, with the 1.5-pixel radius aperture
used to extract the light-curve in orange.
The finder charts are from The Second Digitized Sky Survey (Red); they
are pulled from NASA's \texttt{skyview} service\footnote{See
\url{https://skyview.gsfc.nasa.gov/current/cgi/survey.pl} and
\url{http://archive.stsci.edu/dss/acknowledging.html}}.

@@

Figure~\ref{fig:pg2}.
Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
(\texttt{TF2}), stellar-variability detrended flux, and the background
are shown as a function of barycentric Julian date.  The overplotted
dashed vertical lines are the ephemeris of the highest-power TLS peak
from Figure~\ref{fig:pg1}.  An important visual check is whether the flux
dips are correlated with changes in the background level -- in this
case, they are not.  The standard deviation and TESS magnitude are
quoted in the upper right.  The red line in the second from the top
plot is a spline fit, which in this case was not an essential step for
finding the eclipse signal.

The spline is an optional feature: it is only fitted and removed if
the star is found to be ``variable'' (the Lomb-Scargle peak period is
found with false alarm probability below $10^{-5}$). The spline is a
robust penalized B-spline, which is a B-spline with knot-length
automatically determined via cross-validation
\citep{eilers_flexible_1996}. The idea behind the cross-validation is
that more knots leads to smaller residuals on training data, but
larger errors when tested on the entire dataset.  We used the
\texttt{wotan} implementation, which is a wrapper to the
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
the fit residuals at each iteration
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
number of spline knots was set to 50, which for each TESS sector
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
day}$ window.

@@

Figure~\ref{fig:pg3}.
The plots show the maximally-detrended light-curve (top); the
phase-folded light-curve centered over $\pm3$ transit durations of the
primary transit (middle left); the secondary eclipse (middle right);
the odd-numbered transits (lower left); and the even-numbered transits
(lower right).
Also shown is the best-fit TLS template model --- by default, this
assumes a non-grazing geometry (see \citealt{hippke_TLS_2019}).

The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
from TICv8 when available \citep{stassun_TIC8_2019}.  For the stellar
radius, if TICv8 does not quote a radius, neither will the vetting
report.  If TICv8 gives a stellar radius, but does not give
a stellar mass, we interpolate the mass using the radius and the 
\citet{pecaut_intrinsic_2013}
table, under the assumption that the star is a dwarf.
%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
The effective temperatures calculated by TICv8 were estimated from an empirical
color relation involving Gaia $G_{\rm Bp}$ and $G_{\rm Rp}$ magnitudes.  These
observed colors were dereddened first, using Pan-STARRS dust maps
\citep{green_galactic_2018} for declinations above $-30^\circ$, and the
\citet{schlegel_maps_1998} maps otherwise.

The first eight lines of text are parameters determined from the
best-fitting TLS model.  The one exception is the planet radius, which
uses the stellar radius as noted above.  The ``flux contamination''
(\texttt{TICCONT}) from neighboring stars is {\it never} taken into
account, because transit depth dilution does not affect image
subtraction analyses in the same manner as aperture-photometry
reductions.  The significance of the odd-to-even asymmetry is quoted,
but given the strong rotational variability in this object
(Figure~\ref{fig:pg2}), the apparent odd-even asymmetry could have
been caused by the detrending process.  To estimate the transit to
occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$, the
phase-folded light-curve is also fit by a sum of two gaussians (in
this case, the fit failed).  ``AstExc'' refers to the Gaia-DR2
astrometric excess, which can indicate hints of astrometric binarity
in the system.  ``$d_{\rm geom}$'' is the geometric distance from
\citet{bailer-jones_distances_2018}.  ``$R_\star + M_\star \rightarrow
T_{b0}$'' gives the duration of a zero-eccentricity central transit
based on the TICv8 stellar radius and masses discussed above.

@@

Figure~\ref{fig:pg5}.
The star was considered a candidate cluster member by the source(s)
listed under ``Reference'', in this case
\citet{cantat-gaudin_gaia_2018}.  The name used in their catalog was
\texttt{5325425474687221760}, a Gaia-DR2 identifier, which can be
back-referenced to find the membership probability they assigned this
star for being in Collinder 205.  The base catalog however for this page
of plots is \citet{Kharchenko_et_al_2013}, due to its homogeneous
parameter determination procedure (particularly for age).  If a match to
the \citet{Kharchenko_et_al_2013} catalog is found, then the subplots on
this page are populated; otherwise, they are not.  Top-left shows the
parallax, with orange points sampled from the Gaia-DR2 posterior, black
points the other cluster members in the {\it Kharchenko catalog} (not
the catalog claiming membership), and the blue line the claimed
Kharchenko parallax for the cluster.  A number of field contaminants in
the Kharchenko catalog are visible in this case.  Top-right are the Gaia
proper motions, where against black points are cluster members from
Kharchenko, and the orange is the target star.  Bottom-left is the
color-magnitude diagram, and bottom-right are the on-sky positions.  In
the text, \texttt{N1sr2} is the number of $1\sigma$ cluster members
reported by \citet{Kharchenko_et_al_2013} within the cluster angular
radius; $\log t$ is the base-10 logarithm of the age in years;
\texttt{type} matches the type codes provided by
\citet{Kharchenko_et_al_2013}; ``\texttt{Note}'' gives the description
of the cluster from \citet{Kharchenko_et_al_2013}, if any is available.
Extra caution must be taken when interpreting this set of plots, since
they can only show disagreement between the observed star's properties
and those of the listed Kharchenko members (and the latter may be
incomplete or otherwise biased).

@@

Figure~\ref{fig:pg6}.
This page helps diagnose which stars are producing the observed
variability.  Top-left and top-center are the mean out-of-transit
(OOT) and mean in-transit calibrated images (created separately from our
image-subtraction analysis, using \texttt{TESScut},
\citealt{brasseur_astrocut_2019}).  The OOT images are based on the same
number of exposures as the in-transit images and split evenly before
and after each transit
\citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
The yellow star is the target's position from TICv8; 
small red crosses are WCS-projected locations of neighbor stars.

Middle-left is the most important sub-panel: the difference between
the OOT and in-transit mean images.
If the variability shown in the background map (units: ADU) is off-target,
the signal is not from the target star.  
A two dimensional gaussian is fit to the inner 8x8 pixels to estimate
the centroid position --- the resulting best-fit location is shown as
a white star, and the separation to the catalog star's position
(yellow star) is labelled \texttt{ctlg - gauss(OOT-intra)} on the
right.
A different approach, simply taking the first moment of the middle-left
image, gives the \texttt{ctlg - <OOT-intra>} line.

Middle-center is the same as middle-left, but normalized by the
uncertainty map.  Lower left and lower center show the DSS2-Red field
in linear and log scales at roughly the same pixel scale as the TESS
image, with the 1, 1.5, and 2.25 pixel-radius apertures in blue,
orange, and green respectively.  The brightness of neighborhood stars
is given on the far right.  Note the slight coordinate rotation
difference between DSS and TESS images; DSS images are aligned
north-up, east-left; TESS images are oriented as closely as possible
to this system without actually performing the rotation.

\subsection{Neighborhood plots}
\label{sec:pg7}

Figure~\ref{fig:pg7}.
The analysis in Figure~\ref{fig:pg5} is helpful but insufficient for
determination of cluster membership.
A more thorough approach is to query Gaia-DR2 for
nearby stars in position, parallax, and proper motion space, and
let the data speak for itself regarding {\it (a)} the existence of
the group, and {\it (b)} the target star's membership within the group.

@@

Figure~\ref{fig:pg7} shows the labeled quantities from the target
star, the neighborhood, and the ``cluster members'' reported by
\citet{cantat-gaudin_gaia_2018}, \cite{kounkel_untangling_2019}, or
\citet{Kharchenko_et_al_2013}.  The top three subplots intentionally
omit the labelled cluster members, in order to give the user their own
by-eye assessment of whether they see clusters in the neighborhood,
and whether the target star is within those clusters.
The middle three subplots overplot cluster members from the reference
noted in the legend.

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0001.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit search summary.} See \S~\ref{sec:pg1}.
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0002.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light-curve diagnostics.} See \S~\ref{sec:pg2}.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0003.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit diagnostics.}  See \S~\ref{sec:pg3}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0004.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light-curves for increasing aperture sizes.}  See
    \S~\ref{sec:pg4}.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0005.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Cluster membership assessment diagnostics.} See
    \S~\ref{sec:pg5}.
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{pg_0006.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Imaging variability diagnostics.} See \S~\ref{sec:pg6}.
		\label{fig:pg6}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{pg_0007.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Neighborhood diagnostic.} See \S~\ref{sec:pg7}.
		\label{fig:pg7}
	}
\end{figure*}
